NOSQL\\ BEST PRACTICES

### 2018-04-11 pgconfus2018/presentation.tex
Add an example of multiple detoasting
Update slide title and add work email

@@

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Why to write an extension?}

@@

      \usebeamerfont{subtitle}%
      \fontsize{13pt}{14}\selectfont
      \usebeamercolor[fg]{subtitle}%
        \begin{itemize}[label={}]
            \item {\color{black} \github\ github.com/erthalion}
            \item {\color{black} \twitter\ @erthalion}
            \item {\color{black}\email\ 9erthalion6 at gmail dot com}
        \end{itemize}
      \vspace*{2.5em}%

>>>>

\begin{frame}
    \frametitle{}
    \begin{center}
    \begin{overprint}
    \onslide<1>
    \inputminted[
        fontsize=\Large,
        escapeinside=||
    ]{sql}{sql/detoast_overhead.sql}

    \onslide<2>
    \inputminted[
        fontsize=\Large,
        escapeinside=||
    ]{sql}{sql/detoast_overhead_ok.sql}

    \onslide<3>
    \inputminted[
        fontsize=\Large,
        escapeinside=||
    ]{sql}{sql/detoast_overhead_wrong.sql}
    \end{overprint}

@@

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Why write an extension?}

@@

      \usebeamerfont{subtitle}%
      \fontsize{13pt}{14}\selectfont
      \usebeamercolor[fg]{subtitle}%
        \begin{itemize}[label={}]
            \item {\color{black} \github\ github.com/erthalion}
            \item {\color{black} \twitter\ @erthalion}
            \item {\color{black}\email\ dmitrii.dolgov at zalando dot de}
            \item {\color{black}\email\ 9erthalion6 at gmail dot com}
        \end{itemize}
      \vspace*{2.5em}%
